Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-23 figures_Paper1/energy_setup.tex
Final version 23.08.2022

\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usetikzlibrary{math}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{intersections}
\usetikzlibrary{bending}
\usepgfplotslibrary{fillbetween}

@@

% Figure 1

% \path[>=stealth,<->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=2pt] (2.5,0.5) edge (5,0.5);

% \filldraw[fill=hblue!50!white,draw=hblue,xshift=-2cm,rotate=-90] (-1,0) parabola[bend pos=0.5] bend +(0,2) +(3,0) -- cycle;

\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge (4.7,5.5);

\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\path[>=stealth,line width=1pt] (2.5,2.75) edge (4.5,2.75);

\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge (0,3.5);

\path[>=stealth,line width=1pt] (-2.5,2.25) edge (-0.5,2.25);

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge (-2.7,2.5);

% text

\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};

\node at (5.1,4) {\textcolor{black}{$W_{b}$}};

\node at (3.5,2.6) {\textcolor{black}{$\mu_r$}};  
\node at (-1.5,2.4) {\textcolor{black}{$\mu_l$}};

\node at (-3.1,1) {\textcolor{black}{$W_{b}$}};

\node at (1,2.5) {\textcolor{black}{$\Delta_{\textrm{eff}}$/$\Delta_{\textrm{eff,ph}}$}};

\node at (-2.7,5) {\bfseries(a)};

% Figure 2

\filldraw[draw=hred,fill=hred!20!white] (2.5,-3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,-2.5) -- (0,-3.5);

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-6) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\filldraw[draw=hred,fill=hred!20!white] (-2.5,-6) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text

\node at (3.5,-2) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
\node at (1,-2) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
\node at (1,-5) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
\node at (-1.5,-5) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};

\node at (-1,-2.7) {\textcolor{hyellow}{$\Omega$}};

\node at (-2.7,-1) {\bfseries(b)};

\draw[dotted,color=black,fill=white] (0.5,-5) circle[radius=3pt];

\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=210,line width=1pt] (0.5,-5) edge (0.8,-2);

\draw[color=black,fill=hgreen] (0.8,-2.1) circle[radius=3pt];

\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.8,-2.2) edge (3.2,-2);

% Figure 3

\filldraw[draw=hred,fill=hred!20!white] (2.5,-9) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-9) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,-8.5) -- (-0.2,-9.5);

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-12) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\filldraw[draw=hred,fill=hred!20!white] (-2.5,-12) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text

\node at (3.5,-8) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
\node at (1,-8) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
\node at (1,-11) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
\node at (-1.5,-11) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};

\node at (-1,-8.7) {\textcolor{hyellow}{$\Omega$}};

\node at (-2.7,-7) {\bfseries(c)};

\draw[dotted,color=black,fill=white] (0.5,-11.3) circle[radius=3pt];

\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=240,line width=1pt] (0.5,-11.3) edge (0.4,-7.2);

\draw[dotted,color=black,fill=white] (0.4,-7.3) circle[radius=3pt];

\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=-180,line width=1pt] (0.4,-7.3) edge (1.6,-8);

\draw[color=black,fill=hgreen] (1.6,-8) circle[radius=3pt];

\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (1.6,-8) edge (3.6,-8);

\draw[dotted,color=black,fill=white] (0.9,-10.3) circle[radius=3pt];

\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-150,line width=1pt] (0.9,-10.3) edge (0.7,-8.8);

\draw[color=black,fill=hgreen] (0.67,-8.75) circle[radius=3pt];

\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=210,line width=1pt] (0.7,-8.7) edge (3.6,-8.4);

% \path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.8,-2.2) edge (3.2,-2);

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{math}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{intersections}
\usetikzlibrary{bending}
\usepgfplotslibrary{fillbetween}

@@

% compilation of figure raises warning: Dimension too large, since the axis environment
% is clipped. This is warning can be ignored.
\clip (-3.5,-12.3) -- (5.5,-12.3) -- (5.5,5.3) -- (-3.5,5.3) -- cycle;

% Figure 1
\begin{scope}
% r-lead
% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
\draw[draw=hgreen] (0,2) -- (0,3);
% UHB
\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
\draw[draw=hgreen] (0,3) -- (0,5);
% \draw (0,4) -- (5,4);
% LHB
\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
\draw[draw=hgreen] (0,0) -- (0,2);
% \draw (-3,1) -- (3,1);
% l-lead
% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% r-lead width
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge node[midway,right] {$W_{\text{b}}$} (4.7,5.5);
% % chemical potential right
% \draw[line width=1pt] (2.5,2.75) -- node[midway,below] {$\mu_{\text{r}}$} (4.5,2.75);
%gap
% \path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{eff}}$/$\Delta_{\text{eff},\text{ph}}$} (0,3.5);
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0.5,1.5) edge node[midway,right] {$\Delta_{\text{pg}}$} (0.5,3.5);
% % chemical potential left
% \draw[line width=1pt] (-2.5,2.25) -- node[midway,above] {$\mu_{\text{l}}$} (-0.5,2.25);
% l-lead width
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge node[midway,left] {$W_{\text{b}}$} (-2.7,2.5);

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};

\node at (-2.5,4.5) {\bfseries(a)};
\end{scope}

% r-lead
% (position of lead has to be set manually)
\begin{axis}[%
xmin=0,xmax=3.5,
ymin=-5,ymax=5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
at={(2.5cm,1.15cm)}]

\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);

\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];

\draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
\end{axis}

% l-lead
% (position of lead has to be set manually)
\begin{axis}[%
ymin=-5,ymax=5,
xmin=0,xmax=3.5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
clip mode=individual,
at={(-2.5cm,-1.85cm)}]

\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);

\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];

\draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
\end{axis}

% Figure 2
\begin{scope}[yshift=-6cm]
% % r-lead
% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
\draw[draw=hgreen] (0,2) -- (0,3);
% UHB
\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
\draw[draw=hgreen] (0,3) -- (0,5);
% LHB
\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
\draw[draw=hgreen] (0,0) -- (0,2);
% % l-lead
% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};

\node at (-2.5,4.5) {\bfseries(b)};

% processes

% particles
\draw[dotted,color=black,fill=white] (0.5,1) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.5,3.9) circle[radius=3pt];
% driving
\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=140,in=-140,line width=1pt] (0.5,1) edge (0.5,3.9);
\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
% escape
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.5,3.9) edge (3.2,3.9);

\end{scope}

% r-lead
% (position of lead has to be set manually)
\begin{axis}[%
xmin=0,xmax=3.5,
ymin=-5,ymax=5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
at={(2.5cm,-4.85cm)}]

\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);

\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];

% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
\end{axis}

% l-lead
% (position of lead has to be set manually)
\begin{axis}[%
ymin=-5,ymax=5,
xmin=0,xmax=3.5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
clip mode=individual,
at={(-2.5cm,-7.85cm)}]

\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);

\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];

% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
\end{axis}

% Figure 3
\begin{scope}[yshift=-12cm]
% % r-lead
% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
\draw[draw=hgreen] (0,2) -- (0,3);
% UHB
\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
\draw[draw=hgreen] (0,3) -- (0,5);
% LHB
\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
\draw[draw=hgreen] (0,0) -- (0,2);
% % l-lead
% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm,xshift=0.2cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};

\node at (-2.5,4.5) {\bfseries(c)};

% processes

% particles
\draw[dotted,color=black,fill=white] (0.4,0.7) circle[radius=3pt];
\draw[dotted,color=black,fill=white] (0.4,4.8) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.4,3.25) circle[radius=3pt];
\draw[dotted,color=black,fill=white] (0.9,1.7) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.9,3.25) circle[radius=3pt];
% driving
\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.4,0.7) edge (0.4,4.8);
\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
% impact ionization
\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=60,line width=1pt] (0.4,4.8) edge (0.4,3.25);
\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.9,1.7) edge (0.9,3.25);
% escape
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (0.4,3.25) edge (2.85,3.25);
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=-150,line width=1pt] (0.9,3.25) edge (3.1,3.25);

\end{scope}

% r-lead
% (position of lead has to be set manually)
\begin{axis}[%
xmin=0,xmax=3.5,
ymin=-5,ymax=5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
at={(2.5cm,-10.85cm)}]

\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);

\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];

% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
\end{axis}

% l-lead
% (position of lead has to be set manually)
\begin{axis}[%
ymin=-5,ymax=5,
xmin=0,xmax=3.5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
clip mode=individual,
at={(-2.5cm,-13.85cm)}]

\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);

\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];

% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
\end{axis}

### 2022-08-23 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
Final version 23.08.2022

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill, 
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

@@

\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
xlabel={$\omega/t^{*}$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$el$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$el+ph$};

@@

\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

@@

\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

>>>>

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
ylabel={$A(\omega)$},
legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill, 
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{el};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{el+ph};

@@

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

@@

\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{el};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{el+ph};

@@

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

@@

\addplot[name path=neq_distr_f_filling_hyb0.8O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11ph and xaxis,soft clip={domain=-15:15}];
